\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage[final]{pdfpages}
\usepackage{fancyhdr}
\usepackage{makeidx}
\usepackage{multicol}
\fontencoding{T1}
\pagestyle{fancyplain}
\author{}
\title{Blood-ties and association of the Hunters}
\date{}
\makeindex
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{1pt}
\begin{document}
	\maketitle
	\pagebreak
	\setcounter{tocdepth}{3}
	\tableofcontents
	\pagebreak
	\part{The Families and Groups}
	\section{Asia}
	\subsection{China-East}
	\subsubsection{Raigana}	
	Current Status:
	Powers:
	Physical; Mental; Power; Finesse;
	Head-branch: Imperial Retribution; Dragon Gate
	\pagebreak
	\subsection{China-North}
	\subsection{China-Tibet}
	\subsection{China-West}
	\subsection{India}
	\subsection{Indonesia}
	\subsection{Japan}
	\subsection{Middle East}
	\subsection{Russia-Central}
	\subsection{Russia-East}
	\section{Africa}
	\subsection{Central}
	\subsection{Eastern}
	\subsection{Northern}
	\subsection{Southern}
	\subsection{Western}
	\section{Europe}
	\subsection{Anglo-Saxon}
	\subsection{Baltic}
	\subsection{French}
	\subsection{Germanic}
	\subsection{Greek}
	\subsection{Hispanic}
	\subsection{Italic}
	\subsubsection{The Vatican}
	Located within the Vatican, run by the Pope. Traditional catholic methods for daemon an spirit\\
	elimination, they also have a large group for vampire extermination.\\
	Current Status:\\
	Strong rule in parts of the US of A, Spain, Portugal, Central America and South America. As\\
	such they are mainly active there. Census not available.\\
	Creation Bonus:\\
	Priest: Resolve +1; Composure +1; Occult +3(4)\\
	Hunter: Strength +1; Resolve +1; Occult +3(3)\\
	Powers:\\
	Mental, Power, Exorcism\\
	\pagebreak
	\subsection{Scandinavian}
	\subsubsection{Frosthem}
	Norwegian family, relatively young; dating back to the 8th century. Strong, fast and fearless, using\\
	physical and cold-based powers, though some have been known to user both types of thermal\\
	powers. They prefer using melee weapons, enchanting it with frost.\\
	Current Status:\\
	Strongly decimated by the daemon in the Tunguska-episode. 27 remaining, whereas 4 are\\
	able Aska-users.\\
	Creation Bonus:\\
	Strength +3, Dexterity +1, Size +1\\
	Powers:\\
	Power; Physical; Tjäle (; Aska)\\
	\pagebreak
	\subsubsection{Institutet}
	A collaborate group of engineers and mercenaries, started 1884 on orders of the King of Sweden, Oscar II, to\\
	\begin{quote}\textquotedblleft Skydda hemlandet och dess allierade från övernaturliga makter med fientlig agenda; hemlighålla övernaturlig skeende så den naturliga populationen kan leva ostört\textquotedblright\end{quote}
	\begin{quote}\textquotedblleft Protect the homeland and its allies from supernatural forces with hostile agendas; keep secret the occurrences of supernatural nature so that the natural population can live in peace.\textquotedblright\end{quote} They were deemed a great success, reducing killing and maiming caused by supernaturals in Sweden by over 30\% in the first decade. By the 1950s the group was a well established name within the world of hunters and daemon alike, leaving Sweden mostly ignored.
	Yearly Report:
	Hostile
	Supernatural
	Activity
	Daemon;
	Lowgrade
	Daemon;
	Midgrade
	Daemon;
	Highgrade
	Hunter;
	Rogue
	Spirits;
	Weak
	Spirits;
	Strong
	Immortal;
	Young
	Immortal;
	Old
	Vampire;
	Ghoul
	Vampire;
	Young
	Vampire;
	Old
	Other/
	Unknown
	Encountered 623 223 13 482 52 2 3 2 182 38 12 17
	Eliminated 621 138 6 423 52 2 2 0 42 38 11 2
	Sum: Encountered: 1649  Eliminated: 1337
	Sweden;
	60000
	Norway;
	200000
	Finland;
	200000
	Denmark;
	240000
	The Baltic;
	240000
	Russia;
	300000
	Prussia;
	240000
	Total
	Income 91 840 000 26 000 000 41 200 000 35 440 000 45 760 000 124 500 000 52 060 000 416 800 000
	Yearly (M) 90,1 22,4 32,8 25,6 32,8 65,7 42,7 312
	Missions 29 18 42 41 54 196 39 419
	Expenses 107 769 776 41 295 976 44 830 290 37 464 861 39 942 248 114 820 108 27 438 697 413 561 956
	Research (M) 39,2 16,5 10 13,7 2,1 31,1 2 115
	Education (M) 27,1 10,2 11,7 1,8 2,1 6 2,4 61
	Maintainence (M) 37,8 12,7 16,4 13,6 26 28,5 16,4 151
	Mission Cost avg. 126544 105332 160245 204021 180412 251123 170223 86 261 956
	Total -15 929 776 -15 295 976 -3 630 290 -2 024 861 5 817 752 9 679 892 24 621 303 3 238 044
	Approximated
	Saved Lives 124 411 89 522 147 251 170 002 180 460 732 019 211 523 1 655 188
	Relative HSA (%) 4,60% 6,40% 8,20% 8,50% 8,20% 23,90% 10,6% 10,06%
	Relative B/nSA (%) 720% 411% 373% 346% 484% 102% 291% 389,57%
	\#
	Agents, KIA 129
	Agents, MIA 78
	Civilians, Accidental 153
	Civilians, HSA 138
	Civilians, Injured 18452
	Civilians, Contaminated 3201
	Current Status:
	Highly active protecting regions around Sweden; working on an protection agreement with
	the EU. Recruiting professionals in surveillance, combat and research; internal training program
	with salary, 3-months; 3-year contracts. 6266 active agents.
	Creation Bonus:
	By training program
	Surveillance: Dexterity +2(5); Wits +2(5); Resolve +1(5); Stealth +1(5); Medicine +1(3)
	Requirement: Dexterity 4; Wits 3; Resolve 3; Intelligence 3; Firearms 4; Stealth 3; Investigation 2;
	Weaponry 1; Medicine 1; Athletics 4; Survival 3
	Combat: Dexterity +2(5); Stamina +1(5); Wits +1(5); Resolve +1(4); Firearms +1(5)
	Requirement: Strength 4; Dexterity 3; Firearms 3; Weaponry or Brawl 4; Athletics 3
	Research: Intelligence +1(5); Wits +1(5); Stamina +2(5); Resolve +1(5); Occult +1(4);
	Firearms +1(3); Academics +2(5); Computer, Crafts, Medicine or Science +1(4)
	Requirement: Wits 3; Resolve 3; Intelligence 4; Academics 3; Computer, Crafts, Medicine or
	Science 3
	Power:
	Has regular instructors in all Common powers
	\pagebreak
	\subsubsection{Urskog}
	Believed to have its ancestry in the forests of Norway, Sweden and Finland. They populate large
	parts of Norway, Sweden, Finland and Russia, as well as parts of the Baltic. The Sun is slightly
	harmful to them while in their true form, and thus they mostly stay below ground while not shifted.
	They strongly resemble the legend of trolls in appearance, and it is believed that they are the source
	of the legends. They live in caves and tunnels, miles deep below the ground and inside the
	mountains. They are not naturally able of shapeshifting, but usually teach the basics to their young.
	Resent re-population attempts show they are only able to produce infertile offspring with regular
	humans. These offspring still look positively non-human, and no human mother have survived
	giving birth.
	They are fairly resistant to both warmth and cold, and are known to shrug of lower calibre bullets.
	They have a strong dislike for water and open air.
	Current Status:
	Strongly decimated by the daemon in the Tunguska-episode. No completely accurate census
	available, but assumed between 400 and 600 full-bloods and 30 half-blood .
	Creation Bonus:
	Full-blood: Strength +4, Stamina +4, Resolve +2, Composure +1, Presence +3, Size +3
	Intelligence -1, Wits -2
	Half-blood: Strength +4, Stamina +1, Resolve +1, Size +2
	Powers:
	Physical; Resistance; Fr'gtásth, Shapeshift
	\pagebreak
	\subsection{Slavic}
	\section{North America}
	\subsection{Iroquis}
	\subsection{Aztec}
	\subsection{Canadian}
	\subsection{Cherokee}
	\subsection{Inuit}
	\subsection{Mayan}
	\subsection{Mexican}
	\subsection[US of A - Western states]{US of A \texttwelveudash\ Western states}
	\subsection[US of A - Southern states]{US of A \texttwelveudash\ Southern states}
	\subsection[US of A - Eastern states]{US of A \texttwelveudash\ Eastern states}
	\section{South America}
	\subsection{Argentina}
	\subsection[Brazil - East]{Brazil \texttwelveudash\ East}
	\subsection[Brazil - Central]{Brazil \texttwelveudash\ Central}
	\subsection{Inca}
	\subsection{Western}
	\subsection{Other}
	\subsection{Arctic}
	\subsection{Antarctica}
	\section{Oceania}
	\section{Trekkies}
	\part{Powers}
	\section{Attribute Powers}
	These power can be found almost everywhere, even humans can learn these with some effort.
	If the user have two powers affecting the same attribute, there is a minor bonus (+1).
	Each point will give one bonus die to rolls concerning the specified attribute. With each point the
	character receives one supernatural power concerning the specified attribute.
	When a character achieve level 2 in a power, or receive benefit as if level 2, he count as
	superhuman, and if using it in obvious ways will draw attention.
	When a character achieve level 3 in any power, the difficulty of rolls concerning the specified
	attribute is decreased by 1.
	Level 3 is the maximum achievable.
	\subsection{Finesse}
	Wits; Dexterity; Manipulation
	\subsection{Mental}
	Intelligence; Wits; Resolve
	\subsection{Physical}
	Strength; Dexterity; Stamina
	\subsection{Power}
	Intelligence; Strength; Presence
	\subsection{Resistance}
	Resolve; Stamina; Composure
	\subsection{Social}
	Presence; Manipulation; Composure
	\subsection{Composure}
	\subsubsection{Iron Will}
	? Add one extra success when trying to resist having your will dominated
	? Add two extra success when trying to resist having your will dominated
	? Add two extra success when trying to resist having your will dominated, add +1 to attackers
	difficulty
	\subsection{Dexterity}
	\subsubsection{Fleet of foot}
	? Add +1 Dexterity when calculating speed
	? Add +2 Dexterity when calculating speed
	? Add +4 Dexterity when calculating speed
	\subsubsection{Nimble}
	? Add +1 Dexterity when calculating DV
	? Add +1 DV when calculating DV
	? Add +2 DV when calculating DV
	\subsection{Intelligence}
	\subsection{Calculate}
	? Roll Intelligence+Empathy; if your score exceed the Composure of the target, you attack
	using your Intelligence, if higher than Dexterity
	? Roll Intelligence+Empathy then add 4 successes; if your score exceed the Composure of the
	target, you attack using your Intelligence, if higher than Dexterity
	? Roll Intelligence+Empathy then add 8 successes; if your score exceed the Composure of the
	target, you attack using your Intelligence, if higher than Dexterity
	\subsection{Manipulation}
	\subsection{Lure}
	? Add one extra success when attacking an opponent with whom you have eye-contact
	? Add two extra success when attacking an opponent with whom you have eye-contact
	? Add two extra success attacking an opponent with whom you have eye-contact, you attack
	using the highest of dexterity and manipulation
	\subsection{Presence}
	\subsubsection{Eye of the Serpent}
	Can only be initialized when having eye-contact, if successful, your target can not avert his gaze
	from your eyes.
	? Attempt to force eye-contact with someone, your Presence+Socialize roll is to exceed his
	Composure. If you fail, you cannot attempt again for the remainder of the scene, success
	holds 2 turn.
	? Attempt to force eye-contact with someone, your Presence+Socialize roll is to exceed his
	Composure. If you fail, you cannot attempt again for the next 6 turns, success holds 4 turns.
	? Attempt to force eye-contact with someone, your Presence+Socialize+2 roll is to exceed his
	Composure. If you fail, you cannot attempt again until the next turn, success holds 4 turns.
	\subsection{Resolve}
	\subsubsection{Mental Anvil}
	? Add one extra success when trying to force your will on someone
	? Add two extra success when trying to force your will on someone
	? Add three extra success when trying to force your will on someone
	Stamina
	\subsubsection{Last Stand}
	Enter a last stand; lasting till you or all your opponents are fainted or neutralized, you remain
	immobile for the entire duration, unless you have Fleet of foot 3, by which you can move as if you
	had normal or 5 of speed, whichever is lower. Fleet of foot bonus is nullified. This power also
	enables you to soak damage you might not be able to otherwise.
	? Add +2 DV, nullify 1 damage from all successful attacks against you
	? Add +3 DV, nullify 1 damage from all successful attacks against you
	? Add +3 DV, nullify all bashing and 1 damage from all successful attacks against you
	\subsection{Strength}
	\subsection{Wits}
	\subsubsection{Precognition}
	? Roll DV against unknown attacks, the number of successes is your DV, unless higher then
	your usual DV. Roll difficulty +4
	? Roll DV against unknown attacks, the number of successes is your DV, unless higher then
	your usual DV. Roll difficulty +3
	? Roll DV against unknown attacks, the number of successes is your DV, unless higher then
	your usual DV. Roll difficulty +1
	\subsection{Combination Powers}
	\subsubsection{Heart theft}
	Requirement: 2 superhuman Strength, 3 superhuman Dexterity, Wits 4. For level 2, Occult 6 is
	required.
	In a superhuman display of dexterity and strength, you rip the heart directly from your opponents
	chest.
	? Roll Dexterity + Strength, if the result do not exceed the Stamina + Resolve of the target, it
	was not successful. If successful, the opponent only take damage as if he suddenly has no
	heart.
	? Roll Dexterity + Strength + Occult, if the result do not exceed the Stamina + Resolve of the
	target, it was not successful. If successful you can either choose to play it as per level 1, or
	the target will not take damage until you crush the heart.
	\section{Common Powers}
	\subsection{Shapeshift}
	The power to shift shape, completely reshaping the body. At higher levels users of this power can
	take on much larger or smaller forms than their true shape. The act of shifting takes from some
	seconds to hours; depending on the amount of change, size and expertise.
	\section{Family Powers}
	\subsection{Aska}
	Unique power of the Frosthem family. Rarely seen even among them, possessed by those who have
	reached the height of Tjäle and turned it around, using their previous knowledge to shield
	themselves from the resulting heat-waves. This power is most often used in combination with Tjäle,
	using one of them to shield from the other, enchanting weapons or alternatively heating up and then
	quickly freezing for great effect.
	The highest achieved heat using this power is recorded as 13573°K. The user did not shield himself
	properly and died shortly after.
	\subsection{Exorcism}
	Mainly tought within the Vatican, but found in other areas previously under the rule of the Catholic
	church. Most skills are for protection agains supernaturals and the expulsion of unwelcomed guests
	within human bodies. The greatest feat recorded using this power is holding of 1 S-Grade and 2 AGrade daemons for over 6 seconds, giving the rest of the hunting party the opportunity to die first.
	\subsection{Fr'gtásth}
	Unique power of the Urskog family, making them able to manipulate rock, earth and, to some
	degree, wood. They use the power to create their homes below ground, but it is still a force to fear
	in land-combat. The elders are known to create huge rock-slides and earthquakes. Their power over
	wood lets them forge living weapons, though this is a slow and weary process and is mainly not
	applicable in combat.
	\subsection{Dragon Gate}
	A specialized form of wind-magic, combined with conjuration, tought in the Raigana family, mainly
	to the head-family though those of branch families are tought if deemed worthy and trustworthy.
	The ultimate form bring forth a huge dragon, able of fighting on par with a high-grade daemon,
	effortlessly devouring lesser daemons. On lower levels this power brings forth aspects of the
	dragon, enhancing the body of the caster. There is only one recorded use of the highest level, the
	summoner was instantly devoured and the dragon went on a rampage and was ultimately stopped
	when crossing the Twins.
	\subsection{Imperial Retribution}
	A specialized branch of fire magic, tought in the Raigana family, mainly to the head-family though
	those of branch families are tought if deemed worthy and trustworthy. The ultimate form brings
	down a pillar of fire, devouring only those the caster wishes for. The greatest master known brought
	down a pillar the size of over a square kilometre during the Japanese invasion of China. An entire
	army vanished in less than a second.
	\subsection{Tjäle}
	Unique power of the Frosthem family. Battle-oriented power, giving immunity to cold, normally
	they don't feel the cold until it reach 223°K, some have even been known to survive for hours in
	-120°C. Using this power they can produce cold on will, enchanting or even creating weapons with
	cold. At higher levels they can almost instantaneously freeze large areas, opening great chasms in
	the ground and blowing mountains to bits.
	The lowest achieved cold using this power is recorded as 8°K. The user died seconds after due to
	the heat he was trying to protect himself from.
	\part{Daemons}
	\section{Known Daemons}
	\subsection{Jesus}
	Level: 9 or 10
	Creator: Unconfirmed, JHV or Lucifer suspected
	Age: 27BC
	Appearance: Dark middle eastern, 8 cm long full-beard, dark brown hair down to the cheekbone.
	Large hawk-nose.
	History: Died on the cross claiming to be the son of JHV, ploy by the Armies of Hell to steal
	believers from JHV. Lost a majority of control of believers to the Pope during the upbringing of the
	Catholic church.
	Known Powers: Transform Mater, Resurrection, Air
	Status: Trying to regain power from the Pope
	Recommendation: Disengage, he's lazy and not very combat specialized, beware of bodyguards
	\subsection{JHV}
	Level: 11
	Creator: Unknown
	Age: Unknown, first appearance 5635BC
	Appearance: Unknown
	History: Ancient daemon of unknown descent, operating from outside normal existence,
	commanding vast hordes of minions. God and Lord of the Hebrew, fighting a war against Lucifer
	and the Armies of Hell.
	Known Powers: Dimensional Portal
	Status: Within own dimension
	Recommendation: Engage, you will die anyway
	\subsection{Lucifer}
	Level: 10
	Creator: Unconfirmed, JHV suspected
	Age: Unknown, first appearance 5103BC
	Appearance: Unconfirmed, Shifter
	History: Ancient daemon once under the rule of JHV, leader of successful uprising and later leader
	of the so called Armies of Hell
	Known Powers: Deal With the Devil, Serpents Charm
	Status: Active closing deals with all who's willing to close the deal.
	Recommendation: Do not engage, do not close deal
	\subsection{The Pope}
	Level: Unknown
	Creator: Unknown
	Age: Unknown, first appearance 467AD
	Appearance: Unknown
	History: Established itself within the Catholic Church, stealing believers from Jesus
	Known Powers: Unknown
	Status: Ruling the Vatican, running it as a hunter organization. Quite successful
	Recommendation: Leave it be, it is currently helping our cause
	\subsection{The Twins}
	Level: 10\\
	Creator: Unknown\\
	Age: Unknown, first known appearance 4520BC\\
	Appearance: One boy and one girl, assumed twins. Appear as if 12 years old, golden blond hair,\\
	smooth, round lines. Small neat nose and small pointy chin.\\
	History: Two ancient daemon of unknown descent, operating under a mind-link. Both very\\
	powerful, able of levelling cities but seldom do, no record of widespread destruction since 1506.\\
	Latest known display of power was when devouring a Dragon, summoned using Dragon Gate.\\
	Known Powers: Mind-Link\\
	Boy: Tactical-Vision, Invisibility, Flight, Wind\\
	Girl: Mass-Clone, Earth-Meld, Earthen-Travel, Earth\\
	Status: Low profile, low to none destruction, less than 15 confirmed kills per year.\\
	Recommendation: Do not engage, they only engage when cornered or pissed off.\\
	\section{Daemon Groups}
	\subsection{The Armies of Hell}
	Leader: Lucifer\\
	Members: Jesus
	\pagebreak

	\twocolumn[{\part{Terminology}}]
	\section*{Daemon}
	Also known as Yoki, corrupted souls, evil presence etc. Main target of most hunter-families and groups.
	\paragraph{Grades}
	\subparagraph{X-Grade}
	It has been theorized that there are daemons even stronger than the S-Grade, these are called X-Grade, with a level of 12. As of yet, none of these have ever been recorded. There are sensors active, scanning for these behemoths, prepared to .
	Institutet claims that while these theories are valid, they would be able to bring it down on their own if needed.
	\subparagraph{S-Grade}
	The most dangerous of all known daemon, level
	11. Do not engaged unless armed with an army of
	appropriate size. Last encountered S-Grade caused
	Tunguska. The only known family or group able to
	single-handedly take down one of these without Hbombs are Institutet, and they would suffer heavy
	losses.
	\subparagraph{AAA-Grade}
	Level 9-10. Do not engage unless heavily armed
	and with at least a 40-man strong group.
	\subparagraph{A-Grade}
	Level 7-8. Do not engage without proper
	reconnaissance, go with at least a 12-man strong
	group. These are about as strong as a grand-master
	level hunter.
	\subparagraph{B-Grade}
	Level 5-6. Engage on will, recommendation 6-man
	strong group. These are about as strong as a master
	level hunter.
	\subparagraph{C-Grade}
	Level 3-4. Engage on will, recommendation 4-man
	strong group. These are about as strong as a welltrained hunter.
	\subparagraph{D-Grade}
	Level 2. Engage on will, recommendation 2-man,
	but can often be taken down with a single sniper
	shot. These are about as strong as a hunter.
	\subparagraph{E-Grade}
	Level 1. Engage on will, recommendation 2-man,
	but can most times be taken down with a single
	sniper show. These are about as strong as a hunter.
	\subparagraph{High-Grade}
	Level 8-10.
	\subparagraph{Mid-Grade}
	Level 5-7.
	\subparagraph{Low-Grade}
	Level 1-4.
	\section*{HSA}
	Hostile-Supernatural-Activity, term used to indicate any form of supernatural activity with hostile intent or damaging presence.
	
	\printindex
	
	
\end{document}